cardinalR: Generating interesting high-dimensional data structures

### 2025-11-08 paper-cardinalR.Rmd
Added supplementary section with gen_sum and gen_product

>>>>

# Supplementary numeric generators

Two helper functions, `gen_nproduct()` and `gen_nsum()`, generate numeric vectors of positive integers that approximately satisfy a user-specified target product or sum, respectively.

The function `gen_nsum(n, k)` divides a total sum `n` into `k` positive integers. It first assigns an equal base value to each element and then randomly distributes any remainder, ensuring the elements sum exactly to `n`.

```{r, echo=TRUE}
gen_nsum(n = 100, k = 3)
```

The function `gen_nproduct(n, p)` aims to produce `p` positive integers whose product is approximately `n`. It starts with all elements equal to the rounded $p^{th}$ root of `n` and iteratively adjusts elements up or down in a randomized manner until the product is within a small tolerance of `n`. This accommodates the fact that exact integer solutions for a given product are often impossible.

```{r, echo=TRUE}
gen_nproduct(n = 500, p = 4)
```

### 2025-11-08 paper-cardinalR.tex
Added supplementary section with gen_sum and gen_product

>>>>

\section{Supplementary numeric generators}\label{supplementary-numeric-generators}

Two helper functions, \texttt{gen\_nproduct()} and \texttt{gen\_nsum()}, generate numeric vectors of positive integers that approximately satisfy a user-specified target product or sum, respectively.

The function \texttt{gen\_nsum(n,\ k)} divides a total sum \texttt{n} into \texttt{k} positive integers. It first assigns an equal base value to each element and then randomly distributes any remainder, ensuring the elements sum exactly to \texttt{n}.

\begin{verbatim}
gen_nsum(n = 100, k = 3)
\end{verbatim}

\begin{verbatim}
#> [1] 33 34 33
\end{verbatim}

The function \texttt{gen\_nproduct(n,\ p)} aims to produce \texttt{p} positive integers whose product is approximately \texttt{n}. It starts with all elements equal to the rounded \(p^{th}\) root of \texttt{n} and iteratively adjusts elements up or down in a randomized manner until the product is within a small tolerance of \texttt{n}. This accommodates the fact that exact integer solutions for a given product are often impossible.

\begin{verbatim}
gen_nproduct(n = 500, p = 4)
\end{verbatim}

\begin{verbatim}
#> [1] 4 5 5 5
\end{verbatim}
